\documentclass[10pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[a4paper,margin=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{setspace}

% ---------- Formatting ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagenumbering{gobble}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}{\vspace{6pt}\large\bfseries}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\setlist[itemize]{leftmargin=*,nosep,topsep=2pt}
\setstretch{1.02}

% ---------- Helpers ----------
\newcommand{\resumeItem}[1]{\item #1}
\newcommand{\resumeSubheading}[4]{
  \begin{tabularx}{\textwidth}{X r}
    \textbf{#1} & \textbf{#2} \\
    \textit{#3} & \textit{#4} \\
  \end{tabularx}
}

\begin{document}

% ---------- Header ----------
{\LARGE \textbf{SHAIK ROSHAN JAMEER}} \\
\vspace{2pt}
\faPhone\ +91 7013093226 \hspace{10pt}
\faEnvelope\ \href{mailto:shaikroshan150@gmail.com}{shaikroshan150@gmail.com} \hspace{10pt}
\faMapMarker*\ Hyderabad, India \\
\vspace{2pt}
\faLinkedin\ \href{https://linkedin.com/in/shaik-roshan-jameer-971557322}{linkedin.com/in/shaik-roshan-jameer-971557322}

% ---------- Summary ----------
\section*{Summary}
AI \& Digital Marketing professional with 4+ years of experience in US healthcare revenue cycle operations, now transitioning into AI-powered marketing. Building practical AI tools --- ContentPilot AI and SEOInsight AI --- using React, Node.js, OpenAI and Gemini APIs. Certified in AI for Marketing (AI Business School $\times$ Coursera) and Google Digital Marketing \& E-commerce. Skilled in prompt engineering, AI content creation, SEO strategy, and marketing automation. Strong analytical thinking and process optimisation background from professional operations.

% ---------- Skills ----------
\section*{Skills}
\textbf{AI Tools:} ChatGPT, Claude, Gemini, Perplexity AI, Higgsfield AI, Runway ML, Canva AI \\
\textbf{Digital Marketing:} SEO, Keyword Research, Content Marketing, Content Strategy, Social Media Content, Marketing Automation, Google Analytics \\
\textbf{Specialisations:} Prompt Engineering, AI Content Workflows, AI Video Generation, AI Agents \\
\textbf{Technical:} Python, JavaScript, HTML, CSS, React, Node.js, MongoDB \\
\textbf{Tools:} PHI Phygen, GitHub, Excel, MS Teams \\
\textbf{Soft Skills:} Analytical Thinking, Communication, Process Optimisation, Problem Solving, Team Mentoring

% ---------- Experience ----------
\section*{Experience}

\resumeSubheading
{Senior AR Specialist --- AGS Health Care}{Aug 2023 -- Present}
{Bengaluru, India (Hybrid)}{}
\begin{itemize}
\resumeItem{Managed end-to-end Accounts Receivable processes for US healthcare providers, ensuring timely claims resolution and payment recovery.}
\resumeItem{Investigated denied and underpaid insurance claims --- identifying root causes, coordinating with insurance representatives, and maximising reimbursements.}
\resumeItem{Worked with PHI Phygen and multiple payer portals to resolve complex claim issues while maintaining full compliance with healthcare regulations.}
\resumeItem{Mentored junior team members on denial management, claims follow-up, and revenue cycle best practices.}
\end{itemize}

\resumeSubheading
{AR Specialist --- Elico LTD}{Dec 2020 -- Mar 2022}
{Hyderabad, India}{}
\begin{itemize}
\resumeItem{Managed insurance claim follow-ups and payment collections for Medicare and Medicaid accounts.}
\resumeItem{Resolved denied and pending claims through detailed account analysis and effective communication with insurance providers.}
\resumeItem{Contributed to improving collection performance through proactive follow-ups and timely issue resolution.}
\end{itemize}

% ---------- Projects ----------
\section*{Projects}

\resumeSubheading
{ContentPilot AI --- AI Marketing Content Studio}{2025 -- Present}
{React, Node.js, OpenAI API, Tailwind CSS}{}
\begin{itemize}
\resumeItem{Building an AI-powered web application that generates marketing content (Instagram captions, LinkedIn posts, blog ideas, email copy) in seconds using Generative AI.}
\resumeItem{Implemented content type selection, tone controls, and one-click copy --- reducing content creation time from hours to seconds.}
\end{itemize}

\resumeSubheading
{SEOInsight AI --- AI SEO Assistant}{2025 -- Present}
{React, Node.js, Gemini API, Tailwind CSS}{}
\begin{itemize}
\resumeItem{Building an AI-powered tool that analyses blog articles and generates SEO recommendations including title tags, meta descriptions, keyword suggestions, readability scores, and FAQ schema.}
\resumeItem{Features audit history, reusable content templates, and structured SEO reports designed for content marketers.}
\end{itemize}

% ---------- Certifications ----------
\section*{Certifications}

\resumeSubheading
{AI for Marketing Specialization --- AI Business School $\times$ Coursera}{Jun 2026}
{3 Courses: AI Fundamentals, Practical AI \& Prompting, AI Agents \& Creator Tools}{}

\resumeSubheading
{Google Digital Marketing \& E-commerce Professional Certificate --- Google}{2026}{}{}

\resumeSubheading
{Google AI Essentials --- Google}{2026}{}{}

\resumeSubheading
{Google Prompting Essentials --- Google}{2026}{}{}

% ---------- Education ----------
\section*{Education}

\resumeSubheading
{SV University}{2021 -- 2023}
{Master of Computer Applications (CGPA: 8.0)}{}

\resumeSubheading
{Sri Venkateshwara University}{2018 -- 2020}
{Bachelor of Science in Computer Science (CGPA: 7.5)}{}

% ---------- Activities ----------
\section*{Activities}
\begin{itemize}
\resumeItem{Created AI-generated cinematic video content using Higgsfield AI for marketing and storytelling projects.}
\resumeItem{Passionate about sports, especially cricket, with active participation and interest.}
\resumeItem{Regularly attends tech meetups and follows AI industry developments to stay current with emerging tools and trends.}
\end{itemize}

\end{document}
